---
title: "ADA Midterm Exam Fall 2022"
author: "Leah Nason"
date: "10/20/2022"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Import Data 

```{r import, warning = FALSE, message = FALSE}

# Load relevant packages
pacman::p_load(dplyr, readr, dplyr, tidyverse, graphics, kableExtra, tigerstats)

# Import data from Github 
Data <- read_csv("https://raw.githubusercontent.com/kijohnson/Data/main/titanic.csv")

```

# 2. Find Median Age

```{r analzye, warning = FALSE, message = FALSE}

Data %>%
  group_by(Pclass) %>%
  summarize(Median = median(Age)) %>%
  kbl(col.names = c("Passenger Class", "Median")) %>%
  kable_styling() 

```

# 3. Plot

```{r plot, warning = FALSE, message = FALSE}

# Boxplot
ggplot(Data, aes(x = as.factor(Pclass), y = Age)) +
  geom_boxplot(fill="slateblue") +
  labs(x = "Passengter Class",
       y = "Age",
       title = "Boxplot of Age by Passenger Class") 

# Scatterplot
ggplot(Data, aes(x = Pclass, y = Age)) +
  geom_point() +
  labs(x = "Passenger Class",
       y = "Age",
       title = "Scatterplot of Age by Passenger Class")

# Violin plot
ggplot(Data, aes(x = Pclass, y = Age)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) + # add quartiles
  labs(x = "Self Heart Attack", y = "Life satisfaction",  title = "Violin plot")+
   stat_summary(fun.y=mean, geom="point", shape=23, color="red")+ # add the mean
   stat_summary(fun.y=median, geom="point", shape=2, color="blue") # add median

```

# 4. Find percent males and females by class

```{r analyze, warning = FALSE, message = FALSE}

Table <- rowPerc(xtabs(~Pclass+Sex, data = Data))
ftable(Table)

# Rows represent passenger class 1, 2, and 3
Table %>%
  kbl(col.names = c("Female (percent)", "Male (percent)", "Total (percent)")) %>%
  kable_styling() 

```

# 5. Oops forgot to annotate git steps

### Set up user information
* Leahs-MacBook-Air-2:~ leahnason$ git config --global user.name "Leah Nason"
* Leahs-MacBook-Air-2:~ leahnason$ git config --global user.email leahnason@wustl.edu
* Leahs-MacBook-Air-2:~ leahnason$ git config --list

### Change directory for git repository
* Leahs-MacBook-Air-2:~ leahnason$ cd "/Users/leahnason/Dropbox/My Mac (Leah’s MacBook Air)/Desktop/Fall 2022/Advanced Data Analysis/Midterm/ADA Midterm"

### Initialize a git repository
* Leahs-MacBook-Air-2:ADA Midterm leahnason$ git init
Initialized empty Git repository in /Users/leahnason/Dropbox/My Mac (Leah’s MacBook Air)/Desktop/Fall 2022/Advanced Data Analysis/Midterm/ADA Midterm/.git/

### File is staged
* Leahs-MacBook-Air-2:ADA Midterm leahnason$ git add Midterm.Rmd

### Commit that version with message describing changes 
* Leahs-MacBook-Air-2:ADA Midterm leahnason$ git commit -m 'Version 1'

### Push local files to remote repository
* Leahs-MacBook-Air-2:ADA Midterm leahnason$ git remote add origin git@github.com:leahnason/ADA-Midterm.git
* Leahs-MacBook-Air-2:ADA Midterm leahnason$ git branch -M main
* Leahs-MacBook-Air-2:ADA Midterm leahnason$ git push -u origin main

